---
title: "Get Started"
author: "Ove Haugland Jakobsen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

saiUI is an extension to Shiny that let's you create beautiful layouts with a great user experience using the [Bootstrap 4](https://getbootstrap.com) framework. The package replaces the Bootstrap 3 files with the new Bootstrap 4 framework. The package introduces new functions for creating user interfaces that are compatible with Bootstrap 4.

saiUI is written so that most standard Shiny functions should work as expected. There are however some incompabilities between version 3 and 4 of Bootstrap that will break if you convert a standard Shiny app to saiUI:

* Glyphicons have been removed from Bootstrap 4, and will not render even if you use the `shiny::icon` function (the relevant CSS files are not included)

There are three main layouts included in saiUI. `singlePage()` creates a simple Bootstrap 4 layout with a fluid container. It is an alternative to `fluidPage` from the Shiny package. `saiPage()` is meant as a replacement for `navbarPage` in Shiny. It is built so that you can convert a navbar page to Bootstrap 4 with minimal changes to the code. Because of this, saiUI is *not* compatible with `navbarPage`. The other layout -  `saiDashboard()` - is an alternative to the dashboard layout for the package [shinydashboard](https://github.com/rstudio/shinydashboard) using a custom Bootstrap 4 layout.

## Basic usage

saiUI works in the same way as a standard Shiny application. In the UI file (or your UI definition in `app.R`), you specify the UI function you want to use to render your app. If you want an app with a basic Bootstrap 4 layout, you can use the function `bs4Page()`.

A very basic layout would look like this:

```{r, eval=FALSE}
library(saiUI)

ui <- bs4Page(
  title = 'Demo page',
  div('Hello world!')
)

server <- function(session, input, output) {}

shinyApp(ui = ui, server = server)
```

## Single page

To view an example of the `singlePage()` layout, run the following code in an interactive R session:

```{r, eval=FALSE}
runApp(system.file('examples/01_singlePage', package = 'saiUI'))
```

## Navbar page

To view an example of the `saiPage()` layout, run the following code in an interactive R session:

```{r, eval=FALSE}
runApp(system.file('examples/02_saiPage', package = 'saiUI'))
```

## Dashboard page

```{r, eval=FALSE}
runApp(system.file('examples/03_saiDashboard', package = 'saiUI'))
```
